Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
added part for n 3s in raising order lemma

To show (c), we wish to show that $f := y_{i, e_i}z \in R'$ for $z
\neq y_{i, e_i} \text{ or } y_{i, e_i'}$. Note that $f \in R$ lies
in $R'$ if and only if for all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

@@

By part (a), condition (Ad-ii), and Lemma
~\ref{lem:admissible_inequality} we have
\begin{align*}
	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z)
	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg z \left( \subhalf{e_j'} \right) \\
	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg z \left( \subhalf{e_j'} \right) \\
	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
\end{align*}

>>>>

To show (c), we wish to show, for all generators $z$ of $R'$
such that $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$, that
$f := y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
only if for all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

@@

For the case when $e_j' = 3$ for all $j \in \{1, \ldots, r\}$,
we know that

Otherwise by part (a), condition (Ad-ii), and Lemma
~\ref{lem:admissible_inequality} we have
\begin{align*}
	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z)
	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg z \left( \subhalf{e_j'} \right) \\
	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg z \left( \subhalf{e_j'} \right) \\
	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
\end{align*}
